How the PyPy JIT works

### 2012-03-07 talk/pycon2012/jit/slides.tex
another slide

@@

Resources
\begin{itemize}
\item \#pypy on Freenode
\item http://morepypy.blogspot.com
\item pypy-dev@python.org
\item The Architecture of Open Source Applications, Volume 2
\end{itemize}

>>>>

\begin{frame}{Conclusion}
\begin{itemize}
\item JIT generated from RPython description of interpreter
\item metainterpreter traces hot loops and functions
\item optimizations remove indirection
\item adapt to new runtime information with bridges
\item interpreter optimized for JIT with special hints and data structures
\end{itemize}
\end{frame}

@@

Resources
\begin{itemize}
\item \#pypy on Freenode
\item PyPy sprint
\item http://morepypy.blogspot.com
\item pypy-dev@python.org
\item The Architecture of Open Source Applications, Volume 2 (coming out soon)
\end{itemize}
